Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-02 docs/msr.tex
more on the introduction plus the subsubsections of the Analysis section

We chose to focus our study on the security bugs rather than other
software bugs because compared to the other software bugs,
security bugs have a distinct feature: they are critical. Specifically, a software bug can
lead to a mulfunction of a software application that runs under specific
requirements but a security bug can allow a malicious user to alter the
execution of the entire application. In this case, such bugs could span a wide range
of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Hence, one of the basic pursuits in every new software release should be the
mitigation of such bugs.

@@

\begin{itemize}
	\item the analysis of how security bugs evolve in time. To achieve
this, we inspect every project per version.
	\item the relation of security bugs to the component's size.
	\item bug persistense between versions.
	\item the correlation of security bugs with other bug categories.
	\item the relation of software dependencies and security bugs.
\end{itemize}

@@

>>>>

We chose to focus our study on the security bugs rather than other
software bugs because compared to the other software bugs,
security bugs have a distinct feature: they are critical. Specifically, a software bug can
lead to a mulfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the
execution of the entire application. In this case, such bugs could span a wide range
of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Hence, one of the basic pursuits in every new software release should be the
mitigation of such bugs.

@@

\begin{itemize}
	\item The analysis of how security bugs evolve in time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item The relation of security bugs to the artifact's size.  Here, size is
defined in terms of bytecode.
	\item Security bug persistense between versions. We check if specific bugs are
eliminated between versions.
	\item The correlation of security bugs with other bug categories. We
present how such bugs are correlated with bugs that have to do with
performance, coding practices and others.
	\item The relation of software dependencies and security bugs. Our
hypothesis is that an artifact that is a dependency of many other artifacts
should have a low rate of security bugs. 
\end{itemize}

@@

\subsubsection{How Security Bugs Evolve Over Time}

\subsubsection{The Relation of Defects with the size of an Artifact}

\subsubsection{Persistense of Security Bugs}

\subsubsection{Security Bugs {\sc vs} Other Bug Categories}

\subsubsection{Critical Artifacts and their Defects}
